---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# clarklytics

<!-- badges: start -->
<!-- badges: end -->

The goal of `clarklytics` is to make my life easier while I complete an MBA @ NYU Stern. As I collect functions for various coursework and side business analytics projects, I want to make the most commonly used available to me anywhere.

## Installation

You can install the released version of clarklytics from [github](https://github.com/) with:

``` r
devtools::install_github("bclark86/clarklytics")
```

## Time Value of Money

This is a basic example of the `present_value` function. 

```{r present_value}
library(clarklytics)

clarklytics::present_value(future_value = 1000, rate = 0.05, periods = 5)
```

Here is another one with the par value of a zero coupon bond. 

```{r par_value_tbl}
clarklytics::create_par_value_tbl(face_value = 1000, rate = 0.07)
```


## What's Next?

Not sure. That depends on how classes go. Stay tuned!

